ms_0_intro

### 2018-02-27 man/ms_0_intro.Rmd
update

Remote sensing can be used for studying droughts impacts on ecosystems (*e.g.* @Deshayes2006; @Zhang2013; @AghaKouchak2015; @McDowell2015; @Norman2016). Several studies have analyzed drought impacts on vegetation using remote sensing at different scales [@VicenteSerrano2013; @Panisset2018], and for Mediterranean area there were studies focused on local scales (*e.g* @Lloret2007; @Gouveia2012, @Zribi2016) and recently other covering all Mediterranean region [@Gouveia2017].

>>>>

Remote sensing can be used for studying droughts impacts on ecosystems (*e.g.* @Deshayes2006; @Zhang2013; @AghaKouchak2015; @McDowell2015; @Norman2016). Several studies have analyzed drought impacts on vegetation using remote sensing at different scales [@VicenteSerrano2013; @Panisset2018; @Assal2016], and for Mediterranean area there were studies focused on local scales (*e.g* @Lloret2007; @Gouveia2012, @Zribi2016) and recently other covering all Mediterranean region [@Gouveia2017].
